The Analog Method for Precipitation Downscaling: Finding Better Analog Situations at a Sub-Daily Time Step

### 2016-10-13 Moving temporal window - HESS/template.tex
Adding the replies to referees.
Removing the sharpness and accuracy analysis.

\title{The Analog Method for Precipitation Forecasting: Finding Better Analog Situations at a Sub-Daily Time Step}

@@

\begin{equation}
\label{eq:CRPS}
S_{\text{CRP}} = \int_{-\infty}^{+\infty} \left[ F(y)-\text{H}(y-y^{0})\right]^{2} \text{d}y ,  
\end{equation}
where $\text{H}(y-y^{0})$ is the Heaviside function that is null when $y-y^{0}<0$, and has the value 1 otherwise. \citet{Bontron2004} proposed a decomposition of this score interpreted into a sharpness and an accuracy terms.

@@

\subsubsection{Changes in sharpness and accuracy}

The $S_{\text{CRP}}$ score can be decomposed into two components, namely sharpness and accuracy \citep[see][]{Bontron2004}. The impact of the MTW has been analyzed on these components and the results can be found in Table \ref{table:CRPSS_decomposition_no_recalibration} for the original parameters and in Table \ref{table:CRPSS_decomposition_recalibration} for the re-calibrated methods. The changes are expressed relative to the total $S_{\text{CRP}}$. Both components do not have the same value ranges: accuracy is in our case almost twice the sharpness values. Since the $S_{\text{CRP}}$ is considered here and not the $S_{\text{SCRP}}$, improved prediction capacity results in a lower score. A decrease of the score is thus desirable.

It appears that the sharpness is a bit inferior with the MTW in favor of accuracy (Table \ref{table:CRPSS_decomposition_no_recalibration}). When using the recalibrated parameters, the components are a bit more balanced, but still the accuracy prevails on the sharpness (Table \ref{table:CRPSS_decomposition_recalibration}). Fig. \ref{fig:CRPSS_decomposition_precip_thresholds} illustrates the changes (relative to the total $S_{\text{CRP}}$) in sharpness and accuracy for different precipitation thresholds at the Ulrichen station. Be it for the 2Z or 2Z-2MI method, the original or the recalibrated parameters, the changes are similar: the improvements concern the accuracy over the sharpness, and this to a greater extent for significant precipitation events. The MTW does not allow to improve the sharpness, but the improvement in accuracy is significant, and this especially for the days with heavy precipitation. In terms of the predicted precipitation distribution, it means that the median of the prediction is closer to the observed values, while the distribution is not more condensed than previously.

@@

\begin{figure*}[htb]
	\begin{center}$
		\begin{array}{cccc}
		\includegraphics[width=16cm]{figures/components.pdf}
		\end{array}$
	\end{center}
	\caption{Influence (\%) of the MTW on the $S_{\text{CRP}}$ components (accuracy and sharpness) relatively to the total $S_{\text{CRP}}$, for the 2Z and 2Z-2MI methods, according to different precipitation thresholds. The results are presented for (top) the original parameters, and (bottom) the recalibrated parameters. Improved prediction results in a lower score.}
	\label{fig:CRPSS_decomposition_precip_thresholds}
\end{figure*}

@@

\begin{table}[htb]
	\caption{Changes in sharpness and accuracy relatively to the total $S_{\text{CRP}}$, due to the introduction of the MTW. The changes are presented for both 2Z and 2Z-2MI methods with the original parameters. A decrease of the score is desirable.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
			& Sharpness & Accuracy & Sharpness & Accuracy \\
			\hline
			Ulrichen & 2.82 & -5.29 & 1.00 & -4.30 \\
			Zermatt & 2.26 & -5.01 & 0.88 & -3.58 \\
			Visp & 3.66 & -5.18 & 2.67 & -4.94 \\
			Montana & 1.62 & -2.78 & 0.57 & -2.91 \\
			Sion & 2.02 & -2.78 & 0.33 & -2.75 \\
			Aigle & 0.52 & -2.26 & -1.20 & -2.17 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:CRPSS_decomposition_no_recalibration}
\end{table}

\begin{table}[htb]
	\caption{Same as Table \ref{table:CRPSS_decomposition_no_recalibration} but with the re-calibrated parameters.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
			& Sharpness & Accuracy & Sharpness & Accuracy \\
			\hline
			Ulrichen & 1.44 & -4.56 & -0.37 & -3.34 \\
			Zermatt & 0.80 & -4.03 & 0.75 & -4.42 \\
			Visp & 1.53 & -3.94 & 1.47 & -4.96 \\
			Montana & -0.27 & -1.80 & 0.06 & -3.71 \\
			Sion & 0.95 & -2.66 & -0.10 & -3.19 \\
			Aigle & -0.35 & -2.01 & -2.08 & -1.90 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:CRPSS_decomposition_recalibration}
\end{table}

>>>>

\title{The Analog Method for Precipitation Downscaling: Finding Better Analog Situations at a Sub-Daily Time Step}

@@

\begin{equation}
\label{eq:CRPS}
S_{\text{CRP}} = \int_{-\infty}^{+\infty} \left[ F(y)-\text{H}(y-y^{0})\right]^{2} \text{d}y ,  
\end{equation}
where $\text{H}(y-y^{0})$ is the Heaviside function that is null when $y-y^{0}<0$, and has the value 1 otherwise.

@@

@@

@@
